Crop diversification in a game against nature in a mediterranean agro-ecosystem

### 2020-01-23 risk-percption.Rmd
remove unnecessary calculations

---
title: "Crop diversification in a game against nature"
author: "Nick Gauthier"
date: ""
bibliography: refs.bib 
output: html_document
---

@@

Crop diversification is an excellent example of a widespread and effective regulatory feedback strategy (Figure 1). Relying on a mix of food types with different climatic tolerances is an efficient way to maintain a robust food supply [@helmers2001separating,Anderies2006]. In the Mediterranean, land-use strategies involving a diversified portfolio of wheat and barley have been employed by even the earliest sedentary farmers, and continue to be used to this day [@GOULD1963a,Slafer1999,Abbo2009a,Marston2011190]. Wheat generally has higher yields but is sensitive to water deficits, while barley is less productive but drought tolerant. Planting a mix of wheat and barley, either in the same plot or in a combination of plots, is an effective means of diversifying grain supplies. By adjusting the ratio of wheat to barley, farmers can adapt to changing drought risks.

@@

@@

```{r}
yield_var_wheat <- function(p_dry, p_wet) {
  exp_wheat <- expected_yield_wheat(p_dry, p_wet)
  p_dry * (wheat_dry - exp_wheat) ^ 2 +
    p_wet * (wheat_wet - exp_wheat) ^ 2 +
    (1 - p_dry - p_wet) * (wheat_normal - exp_wheat) ^ 2
}

yield_var_barley <- function(p_dry, p_wet) {
  exp_barley <- expected_yield_barley(p_dry, p_wet)
  p_dry * (barley_dry - exp_barley) ^ 2 +
    p_wet * (barley_wet - exp_barley) ^ 2 +
    (1 - p_dry - p_wet) * (barley_normal - exp_barley) ^ 2
}

yield_var_wheat(0.3, 0.2)
yield_var_barley(0.3, 0.2)
```

```{r}
yield_mad_wheat <- function(p_dry, p_wet) {
  exp_wheat <- expected_yield_wheat(p_dry, p_wet)
  p_dry * abs(wheat_dry - exp_wheat) +
    p_wet * abs(wheat_wet - exp_wheat) +
    (1 - p_dry - p_wet) * abs(wheat_normal - exp_wheat)
  }

yield_mad_barley <- function(p_dry, p_wet) {
  exp_barley <- expected_yield_barley(p_dry, p_wet)
  p_dry * abs(barley_dry - exp_barley) +
    p_wet * abs(barley_wet - exp_barley) +
    (1 - p_dry - p_wet) * abs(barley_normal - exp_barley)
}

yield_mad_wheat(0.3, 0.2)
yield_mad_barley(0.3, 0.2)
```

@@

```{r}
qplot(x = c(300, 400, 500), y = c(0, 1.5, 2), geom = 'line') +
  geom_line(aes(y = c(0.8, 1, 0.5)))
```

@@

```{r}
tibble(wheat_prop = seq(0, 1, .1),
       dry_exp = wheat_prop * wheat_dry + (1 - wheat_prop) * barley_dry,
       normal_exp = wheat_prop * wheat_normal + (1 - wheat_prop) * barley_normal,
      wet_exp = wheat_prop * wheat_wet + (1 - wheat_prop) * barley_wet,
      yield_exp = dry_exp + normal_exp + wet_exp, 
      lower_limit = pmin(dry_exp, normal_exp,wet_exp)) %>%
  ggplot(aes(yield_exp, lower_limit)) +
 # geom_hline(yintercept = nash_eq$utility, linetype = 2)+
#  geom_vline(xintercept = nash_eq$wheat_prop, linetype = 2) +
  geom_line( size = 1.2) +
#  geom_point(data = nash_eq, color = 'black', size = 3) +
 # geom_text(data = nash_eq, 
#            label = paste0('(', nash_eq$wheat_prop, ', ', nash_eq$utility, ')'),
#            nudge_x = 0.1, nudge_y = 0.05) +
  theme_classic()
```

@@

```{r}
calc_ratio <- function(risk) {
  pmax(0, (risk * barley_dry + (risk - 1) * barley_wet) / (risk * (barley_dry - wheat_dry) + wheat_wet * -1 * risk + wheat_wet + barley_wet * (risk - 1)))
}

tibble(risk = seq(0, 1, .01),
       ratio = calc_ratio(risk)) %>%
  ggplot(aes(risk, ratio)) +
  geom_line() + 
  theme_classic()
```

>>>>

---
title: "Crop diversification in a game against nature in a mediterranean agro-ecosystem"
author: "Nick Gauthier"
date: ""
bibliography: refs.bib 
output: html_document
---

@@

Crop diversification is an excellent example of a widespread and effective regulatory feedback strategy (Figure 1). Relying on a mix of food types with different climatic tolerances is an efficient way to maintain a robust food supply [@helmers2001separating,Anderies2006]. In the Mediterranean, land-use strategies involving a diversified portfolio of wheat and barley have been employed by even the earliest sedentary farmers, and continue to be used to this day [@GOULD1963a,Slafer1999,Abbo2009a,Marston2011190]. Wheat generally has higher yields but is sensitive to water deficits, while barley has lower yields and is drought tolerant. Planting a mix of wheat and barley, either in the same plot or in a combination of plots, is an effective means of diversifying grain supplies. By adjusting the ratio of wheat to barley, farmers can adapt to changing drought risks.

@@

```{r}
expand_grid(wheat_prop = seq(0, 1, .01),
       risk = seq(.1, .9, .1)) %>%
  mutate(wheat_exp = wheat_prop * expected_yield_wheat(risk,0),
      barley_exp = (1 - wheat_prop) * expected_yield_barley(risk, 0),
      exp_yield = wheat_exp + barley_exp) %>%
  ggplot(aes(wheat_prop, exp_yield, group = risk, color = risk)) +
  geom_line()
```

@@

@@

@@

@@
